US Korea Exchange Rates \\ STA206 Final Project

### 2014-12-12 paper.tex
Further exploratory work
Discovered bug in Quandl data

Figure~\ref{fig:correlation} shows a histogram of all the pairwise sample
correlations.

@@

>>>>

\subsection{Exploratory Data Analysis}

We started out with some general summary statistics and plotting. The first
issue was missing data, which we had anticipated. While most of the
variables were reported monthly, \texttt{debt} was reported on a quarterly
basis and 
Our simple approach for dealing with this was to
make a plot of these variables over time.
If they are approximately linear then we could 
linearly interpolate with respect to time. The scaled plots 
\ref{fig:na_plot_KOR} and
\ref{fig:na_plot_USA} do appear to be mostly linear, so we interpolated. 
In this plots one can observe that $debt_USA$ is decreasing; this is
because $debt$ carries a sign. The value of $debt_USA$ on

When beginning this project we knew that the time dependency and
multicollinearity would be the
biggest obstacles, since in this case the assumption that the errors
$\epsilon_i \sim N(0, \sigma^2)$ does not hold.
Figure~\ref{fig:scatterplot} shows what the original data looks like.
We observe clear patterns emerging, with some even approaching a
continuous mathematical functional relationship- ie the patterns
between \texttt{gdp}, \texttt{gdp\_deflator}, and \texttt{debt} for Korea.
Figure~\ref{fig:correlation} shows a histogram of all the pairwise sample
correlations for the original data set- they are

Our first approach for overcoming this time dependence was to create a new
data frame from the original data by taking the difference between each
subsequent row. More formally, if our original design matrix $X$ is $n
\times p$ then we can define a new $n - 1 \times p$ matrix $\tilde{X}$ by
setting
\[
    \tilde{X_{i,*}} = X_{(i + 1), *} - X_{i, *}
\]
for $i = 1, 2, \dots, n-1$ where $X_{i, *}$ represents the $i$th row of
$X$.

This approach did indeed eliminate the most obvious patterns, but 
sacrifices interpretability

Our first step was to separate the data into training and validation sets,
and only

@@

\begin{figure}
  \centering
    \includegraphics{na_plot_USA.pdf}
  \caption{Scaled variables with NA values}
  \label{fig:na_plot_USA}
\end{figure}

\begin{figure}
  \centering
    \includegraphics{scatterplot.pdf}
  \caption{Scatterplot of untransformed data}
  \label{fig:scatterplot}
\end{figure}
